Minimizing post shock forecasting error using disparate information

### 2020-06-08 manuscript/manuscript.tex
corrected R codes for simulation and updated manuscript for simulation

\textbf{I think that our bootstrap procedure should first sample the disparate time series without replacement, and then estimate the parameters in each resampled time series.}
The formal steps of our bootstrap procedures are outlined in the Supplementary Materials, the intuition for our procedure is as follows: let $B$ be the bootstrap sample size and initialize $y_{i,0}$ for all $i = 2,\ldots,n+1$. At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i = 2,\ldots,n+1$. Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$. We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$. Therefore, this parametric bootstrap framework will work for us.
Once can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.

Let 
$
  \overline{\hat{\alpha}_{\mrm{aadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
$, 
$
  \overline{\hat{\alpha}_{\mrm{wadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
$, 
and 
$
  \overline{\hat{\alpha}_{\mrm{IVW}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
$
The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold. The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}}
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
  =\E{\hat{\alpha}_{\rm wadj}|\Theta},
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator is similar. The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$. However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is a linear combination of OLS estimates with random weights. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.

@@

We stress that the above approximation is conditioned on $\Theta$ and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$. %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population. For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$. 
Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.

@@

\subsection{Parametric bootstrap simulation}
\label{parametricbootstrapsimulation}

In this section, we provide experiments that vary across variance of $\alpha_i$, $y_{i,t}$, and donor pool size $n$ using two bootstrap techniques with one conditioned on the donor pool and one without. We implement our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$. We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers. It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Moreover, $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.

@@

For the use of our methodology, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest.

>>>>

To specify, there are two possible parametric bootstrap procedures for our methods, one conditioned on donor pool and the other  without. We first illustrate the simpler parametric bootstrap conditioned on the donor pool. The formal steps of it are outlined in the Supplementary Materials, the intuition for our procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool. initialize $y_{i,0}$ for all $i \in I$. At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$. Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$. We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$. Therefore, this parametric bootstrap framework will work for us.
Once can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.

The parametric bootstrap without conditioning on the donor pool differs from the one with in the step that the former performs a non-parametric bootstrap by sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^*$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^*$.

Let 
$
  \overline{\hat{\alpha}_{\mrm{adj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
$, 
$
  \overline{\hat{\alpha}_{\mrm{wadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
$, 
and 
$
  \overline{\hat{\alpha}_{\mrm{IVW}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
$
The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold. The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}}
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
  =\E{\hat{\alpha}_{\rm wadj}|\Theta},
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator is similar. The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$. However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is a linear combination of OLS estimates with random weights. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.

@@

We stress that the above approximation is conditioned on $\Theta$ and the donor pool, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$. %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population. For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$. 
For parametric bootstrap without conditioning on the donor pool but conditioned on $\Theta$, we stress that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold. Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.

@@

In this section, we provide justification for our methods based on simulation examples. We implement our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers. It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Moreover, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well. We consider $p=2$ and $\mu_{\alpha}=10$. In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\gamma}$ and $\sigma_{\delta}$ in the model $\delta_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\delta}\mathbf{I}_p}$, and $\gamma_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\gamma}\mathbf{I}_p}$.

\subsection{Parametric bootstrap simulation for risk-reduction propositions}
\label{parametricbootstrapsimulation}

In this section, we provide justification for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}). We will compare the result of using parametric bootstrap conditioned on the donor pool with the one without using the parameter setup discussed in Section \ref{simulation}.

Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions. We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation. Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise. Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table. 
\begin{center}
  \begin{center}
      \begin{tabular}{cc|c|c}
        \hline
        & & \multicolumn{2}{c}{Decision} \\
        & & Accept $\hat{\alpha}$ & Reject $\hat{\alpha}$ \\ 
                \hline
     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
      \cline{3-4}
      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
      \hline
      \end{tabular}
  \end{center}
\end{center}
We report 1 for risk-reduction propositions to be consistent and 0 otherwise.

\subsection{Simulation for prediction}

In this section, we report prediction results for our methods in the simulation. Specifically, we are interested in the distance between $\alpha_1$ and our shock-effect estimators, and the distance between $y_{1,T_1^*+1}$ and $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$.

@@

For the use of our methodology, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest. We recommend using parametric bootstrap without conditioning on the donor pool when the donor pool size $n$ is large, and the one conditioned on the donor pool when $n$ is small.
